---
author: Parsa Khayatzadeh
title: Systems Engineering Ph.D. student @ Cornell 
format:
  classic-cv-pdf: default
cvfooter:
  left: "parsakhay.com"
  right: "github.com/parsakhay"
cvcolor: 58748F #without `#`
cvfont: raleway #texlive fonts like raleway,fetamont,gillius,comfortaa
cvmeta:
  - title: Ph.D. Student
    left: Systems Engineering, Cornell University
    right: Ithaca, NY
  - title: "Supervisior:"
    left: Prof. Michael Charles
  - title: Research Area
    left: Computational Sustainability
    right: mr.schochastics.net
  - title: Techs
    left: IAMs, Human-Earth Systems, Julia, R
    right: pk525@cornell.edu
execute:
  echo: false
---

```{r}
#| label: cvevents
cvevents <- function(tbl, when, what, where, details) {

    command_start <- "\\cvevent"

    res <- paste0(
        command_start, "{", tbl[[when]], "}", 
        "{", tbl[[what]], "}",
        "{", tbl[[where]], "}")
    
    tbl[[details]] <- sapply(tbl[[details]], function(x) paste0("{", x, "}", collapse = ","))
    res <- paste0(res, "{",tbl[[details]],"}")

    cat(res, sep = "\n")
}
```

# Summary

I have started my Ph.D. at Cornell as a Systems Engineering student under the supervision of Prof. Michael Charles. I am interested in design aspect of human-earth models. I link different modules of the system to provide a narrative of plausible futures of the world. My current research focuses on the downscaled study of IAMs aimed to serve tribal governed communities and my case study is Navajo Nation.  

# Experience


```{r}
#| label: experience
#| output: asis
tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
    "Team Lead", "GESIS - Leibniz Institute for the Social Sciences", "Mar. 2022 - Present",
    "Transparent Social Analytics, Department of Computational Social Science", c("Coordination of a project to build an Open Science platform with reusable code and tutorials", "Research on Open Science Practices", "Implementation of tools to enhance reproducibility and facilitate research with digital data in R"),
    "Presidential Fellow", "University of Manchester", "Sep. 2018 - Feb. 2022",
    "Sociology Department", c("Research on Disinformation on Social Media", "Analyses of large scale and unstructured data sets with R, Python and Bash"),
    "Post Doctoral Researcher", "ETH Zurich", "Nov. 2017 - Aug. 2018", "Chair of Social Networks", c("Developing new methods to analyze social networks", "Implementing methods in libraries", "Gathering and analyzing large datsets from Social Media APIs"),
    "Post Doctoral Researcher", "University of Konstanz", "Oct. 2015 - Oct. 2017", "Department of Computer & Information Science", c("Developing new methods to analyze social networks", "Implementing methods in libraries", "Webscraping and harmonizing a large corpus of football data"),
    "Ph.D. Candidate", "University of Konstanz", "Nov. 2012 - Sep. 2015", "Department of Computer & Information Science", c("Developing new methods to analyze social networks", "Implementing methods in libraries")
) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

# Education

```{r }
#| label: education
#| output: asis
tibble::tribble(
    ~degree, ~uni, ~loc, ~dates, ~details,
    "Ph.D. in Systems Engineering", "Cornell University", "Ithaca, NY", "Aug. 2023 - Current", c("Thesis: A Positional Approach for Network Centrality", "Developed and implemented new methods to assess network centrality"),
    "B.Sc. in Industrial Engineering", "University of Tehran", "Tehran, Iran", "Aug. 2018 - Jul. 2022", c("Thesis: PV vs. CSP: a solar renewable technology review and electricity cost analysis based on improvised LCOE", "Implementation and comparison of different clustering algorithms using Matlab")
) |>
    cvevents(when = "dates", what = "degree", where = "loc", details = "details")
```
