---
author: Parsa Khayatzadeh
title: pk525@cornell.edu
format:
  classic-cv-pdf: default
cvfooter:
  left: "parsakhay.com"
  right: "github.com/parsakhay"
cvcolor: 58748F #without `#`
cvfont: comfortaa #texlive fonts like raleway,fetamont,gillius,comfortaa
cvmeta:
  - title: Position
    left: Ph.D. Student in Systems Engineering, Cornell University
    right: Ithaca, NY
  - title: Supervisior
    left: Prof. Michael Charles
  - title: Research Area
    left: Computational Sustainability
    right: parsakhay.com/research
  - title: Research Interset
    left: IAMs, Human-Earth Systems, Shared Socioeconomic Pathways, Sustainable Computing 
execute:
  echo: false
---

```{r}
#| label: cvevents
cvevents <- function(tbl, when, what, where, details) {

    command_start <- "\\cvevent"

    res <- paste0(
        command_start, "{", tbl[[when]], "}", 
        "{", tbl[[what]], "}",
        "{", tbl[[where]], "}")
    
    tbl[[details]] <- sapply(tbl[[details]], function(x) paste0("{", x, "}", collapse = ","))
    res <- paste0(res, "{",tbl[[details]],"}")

    cat(res, sep = "\n")
}
```

# Summary

I have started my Ph.D. at Cornell as a Systems Engineering student under the supervision of Prof. Michael Charles. I am interested in design aspect of human-earth models. I link different modules of the system to provide a narrative of plausible futures of the world. My current research focuses on the downscaled study of IAMs aimed to serve tribal governed communities and my case study is Navajo Nation.  

# Education

```{r }
#| label: education
#| output: asis
tibble::tribble(
    ~degree, ~uni, ~loc, ~dates, ~details,
    "Ph.D. in Systems Engineering", "Cornell University", "Ithaca, NY", "Aug. 2023 - Present", list("Area: Computational Sustainability","Advisor: Prof. Michael Charles"),

    "B.Sc. in Industrial Engineering", "University of Tehran", "Tehran, Iran", "Aug. 2018 - Jul. 2022", list("Advisor: Prof. Hossein Iranmanesh","Final Project: PV vs. CSP: a solar renewable technology review and electricity cost analysis based on improvised LCOE", "Course Highlights: Operations Research  -  System Analysis  -  Engineering Statistics  -  Fundamentals of Probability  -  Microeconomic Theory  -  Macroeconomics  -  Statistical Quality Control  -  Decision Analysis")
) |>
    cvevents(when = "dates", what = "degree", where = "loc", details = "details")

```


# Academic Experience


```{r}
#| label: experience
#| output: asis
tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
    "Research Assistant", "Cornell University", "Aug. 2023 - Present", "",c("Advisor: Michael Charles","Downscaled Integrated Assessment models"),

    "Teaching Assistant", "Cornell University", "Aug. 2024 - Dec. 2024", "",c("Professor: Natalie Cápiro","Engineering Processes for Environmental Sustainability"),

    "Teaching Assistant", "University of Tehran", "Aug. 2019 - Jul. 2022",
    "", list("Courses: Simulation Principles  - Probability and Applications - Microeconomics - Macroeconomics - System Analytics"),

   "Summer Research Intern", "UT's Research Institute for Energy Management and Planning", "Aug. 2021 - Jul. 2022",
    "", list("A feasibility study of solar technologies with a focus on CSP technologies | Supervisor: Dr. Hossein Iranmanesh"),

) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```

# Extracurricular Activities

```{r}
#| label: Extracurricular Activities
#| output: asis
tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
    "Scientific  Association of Industrial Engineering at University of Tehran", "UTIESA", "Aug. 2019 - Jul. 2021", "", c("Board Member", "Managing Editor of Fankaav Stident Journal","Award: Harekat, University's best student journal in 2022")

) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```
