---
author: Parsa Khayatzadeh
title: Systems Engineering Ph.D. student @ Cornell 
format:
  classic-cv-pdf: default
cvfooter:
  left: "parsakhay.com"
  right: "github.com/parsakhay"
cvcolor: 58748F #without `#`
cvfont: raleway #texlive fonts like raleway,fetamont,gillius,comfortaa
cvmeta:
  - title: Ph.D. Student
    left: Systems Engineering, Cornell University
    right: Ithaca, NY
  - title: "Supervisior:"
    left: Prof. Michael Charles
  - title: Research Area
    left: Computational Sustainability
    right: mr.schochastics.net
  - title: Techs
    left: IAMs, Human-Earth Systems, Julia, R
    right: pk525@cornell.edu
execute:
  echo: false
---

```{r}
#| label: cvevents
cvevents <- function(tbl, when, what, where, details) {

    command_start <- "\\cvevent"

    res <- paste0(
        command_start, "{", tbl[[when]], "}", 
        "{", tbl[[what]], "}",
        "{", tbl[[where]], "}")
    
    tbl[[details]] <- sapply(tbl[[details]], function(x) paste0("{", x, "}", collapse = ","))
    res <- paste0(res, "{",tbl[[details]],"}")

    cat(res, sep = "\n")
}
```

# Summary

I have started my Ph.D. at Cornell as a Systems Engineering student under the supervision of Prof. Michael Charles. I am interested in design aspect of human-earth models. I link different modules of the system to provide a narrative of plausible futures of the world. My current research focuses on the downscaled study of IAMs aimed to serve tribal governed communities and my case study is Navajo Nation.  

# Education

```{r }
#| label: education
#| output: asis
tibble::tribble(
    ~degree, ~uni, ~loc, ~dates, ~details,
    "Ph.D. in Systems Engineering", "Cornell University", "Ithaca, NY", "Aug. 2023 - Current", list("Area: Computational Sustainability"),
    "B.Sc. in Industrial Engineering", "University of Tehran", "Tehran, Iran", "Aug. 2018 - Jul. 2022", list("Thesis: PV vs. CSP: a solar renewable technology review and electricity cost analysis based on improvised LCOE", "Course Highlights: Operations Research \\textbullet\\ System Analysis \\textbullet\\ Engineering Statistics \\textbullet\\ Fundamentals of Probability \\textbullet\\ Microeconomic Theory \\textbullet\\ Macroeconomics \\textbullet\\ Statistical Quality Control \\textbullet\\ Decision Analysis")
) |>
    cvevents(when = "dates", what = "degree", where = "loc", details = "details")

```


# Experience


```{r}
#| label: experience
#| output: asis
tibble::tribble(
    ~role, ~institution, ~dates, ~details, ~tasks,
    "Teaching Assistant", "Cornell University", "Aug. 2024 - Dec. 2024", "",c("Professor: Natalie Cápiro","Engineering Processes for Environmental Sustainability"),

    "Teaching Assistant", "University of Tehran", "Aug. 2019 - Jul. 2022",
    "", c("Courses: Simulation Principles \\textbullet\\Probability and Applications\\textbullet\\Microeconomics\\textbullet\\Macroeconomics\\textbullet\\System Analytics"),

    "Board Member", "Scientific Association of Industrial Engineering, University of Tehran (UTIESA)", "Aug. 2019 - Jul. 2021", "", c("Developing new methods to analyze social networks", "Implementing methods in libraries", "Gathering and analyzing large datsets from Social Media APIs"),

) |>
    cvevents(when = "dates", what = "role", where = "institution", details = "tasks")
```